Flowchart of Current Algorithm

### 2008-10-24 docs/flowchart/flowchart.tex
fix a section reference

Compute $\dt$ for the next time step with the procedure described in \S~ref{sec:timesteps},
using $w_0$ as computed in step 6 and
$\Ubt^{n+1}$ as computed in step 11.  We use this $\dt$ in the next time step.

>>>>

Compute $\dt$ for the next time step with the procedure described in \S 3.4 of paper III
using $w_0$ as computed in step 6 and
$\Ubt^{n+1}$ as computed in step 11.  We use this $\dt$ in the next time step.
